MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-02-19 cmc-rnaseq-de/HBCC_ACC-Nirmala_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
store adjusted fit dream output obj

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_ACC-Nirmala_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_ACC-Nirmala_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

>>>>

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_ACC-Nirmala_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_ACC-Nirmala_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store adjusted fit linear mixed model object as RDS
saveRDS(ADJUSTED.FIT, file = 'CMC_ACC_DLPFC_dream-output.rds')
ADJ_OBJ = File('CMC_ACC_DLPFC_dream-output.rds',
               name = 'Dream Output object', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```

### 2020-02-19 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
store adjusted fit dream output obj

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_ACC-STG_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_ACC-STG_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

>>>>

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_ACC-STG_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_ACC-STG_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store adjusted fit linear mixed model object as RDS
saveRDS(ADJUSTED.FIT, file = 'CMC_ACC_DLPFC_dream-output.rds')
ADJ_OBJ = File('CMC_ACC_DLPFC_dream-output.rds',
               name = 'Dream Output object', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```

### 2020-02-19 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
store adjusted fit dream output obj

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

>>>>

# Store enrichment results
write.table(enrichment.results, file = 'CMC_HBCC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_HBCC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'enrichResults'
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store adjusted fit linear mixed model object as RDS
saveRDS(ADJUSTED.FIT, file = 'CMC_ACC_DLPFC_dream-output.rds')
ADJ_OBJ = File('CMC_ACC_DLPFC_dream-output.rds',
               name = 'Dream Output object', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```

### 2020-02-19 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
store adjusted fit dream output obj

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

>>>>

# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store adjusted fit linear mixed model object as RDS
saveRDS(ADJUSTED.FIT, file = 'CMC_ACC_DLPFC_dream-output.rds')
ADJ_OBJ = File('CMC_ACC_DLPFC_dream-output.rds',
               name = 'Dream Output object', 
               parentId = CODE$properties$id)
ADJ_OBJ = synStore(ADJ_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ADJ_OBJ, annotations = all.annotations)
```
